A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Simplify the keywords
Add conclusion for experiement

\begin{IEEEkeywords}
publish/subscribe, data trading, decentralization, Distributed Ledger Technology
\end{IEEEkeywords}

@@

Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods. Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively. The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data. The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.

>>>>

\begin{IEEEkeywords}
subscription model, decentralization, data monetization
\end{IEEEkeywords}

@@

Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods. Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively. The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data. The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range. Under our design which delegate MAM operations with Tangle-accelerator and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy. E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.
